Individual and Differential Harm in Redistricting

### 2025-08-25 paper/harm.qmd
typo
part discloc through sec 3

The harm framework combines two key ideas, further motivated in @sec-motivation.
First, it operates at the level of the individual voter and measures whether each voter is represented by the candidate of their choice.
This unifies gerrymandering analyses across contexts and reflects the goal that elected officials represent the preferences of the voting public [see also @brunell2010].
Few existing measures, with the exception of partisan disclocation [@defoeubarodd21], are focused on the invididual voter this way.

@@

Harm requires both terms to be true: the first measuring if a voter is not represented by their chosen candidate under $q$, and the second term measuring if they would have been represented by their chosen candidate under the counterfactual plan $\tilde q$.

>>>>

The harm framework combines two key ideas, further motivated in @sec-motivation.
First, it operates at the level of the individual voter and measures whether each voter is represented by the candidate of their choice.
This unifies gerrymandering analyses across contexts and reflects the goal that elected officials represent the preferences of the voting public [see also @brunell2010].
Few existing measures are focused on individual voters this way.
The exception is partisan dislocation [@defoeubarodd21], which compares the partisanship of a voter's district with the partisanship of their nearest neighbors.

@@

Harm involves two terms: the first measuring if a voter is not represented by their chosen candidate under $q$, and the second term measuring if they would have been represented by their chosen candidate under the counterfactual $\tilde q$.
This comparison differs from the one that underlies partisan dislocation [@defoeubarodd21], where the comparison is against a group of neighboring voters rather than an alternative plan.
We discuss this difference more in [Appendix @sec-connections], and compare the two measures empirically in @sec-nj.
